---
title: "R Notebook on Linear Regression Lab"
output: html_notebook
---

```{r}
install.packages('ISLR')
#installing the package
```

```{r}
#importing the packages
library(ISLR)
library(MASS) 
```

# Simple Linear Regression

```{r}
#previewing boston dataset and fixing
fix(Boston)
```

```{r}
#column informations for the dataset
names(Boston)
```

```{r}
#attaching the dataset and fitting the linear model
attach(Boston)
lm.fit = lm(medv~lstat,data=Boston)
```

```{r}
summary(lm.fit)
```

```{r}
names(lm.fit)
```

```{r}
coef(lm.fit)
```

```{r}
confint(lm.fit)
```

```{r}
predict(lm.fit,data.frame(lstat=(c(5,10,15))), interval="confidence") #confidence intervals
```

```{r}
predict(lm.fit,data.frame(lstat=(c(5,10,15))), interval="prediction") #prediction intervals
```

```{r}
plot(lstat,medv) #plotting the variables
abline(lm.fit,lwd=3) #generating regression lines
```

```{r}
#making it colourfull
plot(lstat,medv,col='navy')
abline(lm.fit,lwd=3,col='red')
```

```{r}
#process to change shapes in the plot
plot(lstat,medv,pch=20)
```

```{r}
#another kind of shape
plot(lstat,medv,pch="+")
```

```{r}
#'pch' is the command
plot(1:20,1:20,pch=1:20)
```

```{r}
#dividing the plotting in 2x2 grids using 'par(mfrow=)'
par(mfrow=c(2,2))
plot(lm.fit)
```

```{r}
#computing residual plot
plot(predict(lm.fit), residuals(lm.fit))
```

```{r}
#stundentized residuals=quotient resulting from the division of a residual by an estimate of its standard deviation.
plot(predict(lm.fit), rstudent(lm.fit))
```

```{r}
#a suite of functions that can be used to compute some of the regression (leave-one-out deletion) diagnostics, for the VGLM class
plot(hatvalues(lm.fit))
```

```{r}
#identifying largest element of a factor
which.max(hatvalues(lm.fit))
```

# Multiple Linear Regression

```{r}
#fitting the multiple linear model
lm.fit=lm(medv~lstat+age,data=Boston)
summary(lm.fit)
```

```{r}
#fitting all predictors to output variable using
lm.fit=lm(medv~.,data=Boston)
summary(lm.fit)
```

```{r}
#importing Companion to Applied Regression package
library(car)
```

```{r}
#variance inflation
vif(lm.fit)
```

```{r}
#except age all predictors will show
lm.fit1=lm(medv~.-age,data=Boston)
summary(lm.fit1)
#alternately: lm.fit1=update(lm.fit, ~.-age)
```

```{r}
plot(lm.fit1)
```

# Interaction Terms

```{r}
summary(lm(medv~lstat*age,data=Boston))
```

# Non-linear Transformations of the Predictors

```{r}
#lm() fn can also accomodate non linear transformations
lm.fit2=lm(medv~lstat+I(lstat^2))
summary(lm.fit2)
```

**The near-zero p value suggests that the model performs better.**

We will now run anova() to see which quadratic fit is superior

```{r}
lm.fit=lm(medv~lstat)
anova(lm.fit,lm.fit2)
```

*From here we see that fit2 is much superior.*

```{r}
#plotting
par(mfrow=c(2,2))
plot(lm.fit2)
```

```{r}
lm.fit5=lm(medv~poly(lstat,5)) #creating polynomial inside lm
summary(lm.fit5)
```

```{r}
summary(lm(medv~log(rm),data=Boston)) #summary
```

# Qualitative Predictors

```{r}
#loading and previewing carseats data
fix(Carseats)
```

```{r}
names(Carseats)
```

```{r}
lm.fit=lm(Sales~.+Income:Advertising+Price:Age,data=Carseats)
summary(lm.fit)
```

```{r}
?Contrasts #to learn about contrasts
```

### Description

These are substitutes for similarly named functions in the **stats** package (note the uppercase letter starting the second word in each function name). The only difference is that the contrast functions from the **car** package produce easier-to-read names for the contrasts when they are used in statistical models.

The functions and this documentation are adapted from the **stats** package.

```{r}
attach(Carseats)
contrasts(ShelveLoc) #retur the coding that r uses for dummy variables
```

# Writing Functions

**Now we will learn how to create functions**

```{r}
#first assigning the fn name
LoadLibraries=function(){
 library(ISLR)
 library(MASS)
 print("The libraries have been loaded.")
 }
```

```{r}
#now just put the name and see the fn
LoadLibraries
```

```{r}
LoadLibraries()
```

***Chapter 3 ends.***
